\documentclass[11pt, a4paper]{article}

\usepackage[a4paper, margin=1.0in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{tgpagella} 
%\usepackage{indentfirst}
\usepackage{fancyhdr}
\setlength\parindent{0pt}
\usepackage{hyperref}
\urlstyle{same}

\usepackage{xcolor}
\definecolor{dark-blue}{rgb}{0.15, 0.15, 0.4}

\usepackage{sectsty}
\sectionfont{\large\bf\uppercase}

\usepackage{titlesec}
\titlespacing*{\section}{0.0em}{0.2em}{0.0em}

\usepackage{enumitem}
\setlist[itemize]{leftmargin=0.5in, itemsep=-0.5\parsep, topsep=-0.5\parskip}
\setlist[enumerate]{leftmargin=0.5in, itemsep=-0.5\parsep, topsep=-0.5\parskip}


\renewcommand{\baselinestretch}{1.04}
%\setlength{\parskip}{0.4em}
\newcommand\nl[1]{\item[] {#1}}
\newcommand\ml[1]{\item[--] {#1}}
\newcommand\pl[1]{\vspace{-0.2em}\begin{sloppypar}{#1}\end{sloppypar}}
\newcommand{\hr}{\hrule\vspace{0.5em}}
\newcommand{\me}{\textbf{Jieyu Zhao}}

\pagestyle{plain} %empty
\rhead{Last Updated: \today}
\renewcommand{\headrulewidth}{0pt}

\begin{document}
\thispagestyle{fancy}	

\begin{center}
	{\large \bf Jieyu Zhao}
\end{center}
\begin{center}
	{PHE \#332, USC, Los Angeles, CA | \url{https://jyzhao.net} | {jieyuz@usc.edu}}
\end{center}

%----------------------------------------------------------------------------------------
%	Research Interests
%----------------------------------------------------------------------------------------
\section*{Research Interests}
\hr
\begin{itemize}
\item Detecting potential stereotypes in machine learning models
\item Developing computational approaches to enhance the fairness in NLP applications
\end{itemize}


%----------------------------------------------------------------------------------------
%	Education
%----------------------------------------------------------------------------------------
\section*{Education and Experience}
\hr
\textbf{Assistant Professor. University of Southern California}, CA, USA \hfill{2023.08 - Current}

\textbf{Postdoc. University of Maryland, College Park}, MD, USA \hfill{2022.01 - 2023.08}
 \begin{itemize}[leftmargin=20pt]
	\item[] UMD Institute for Advanced Computer Studies
 \item[] CLIP Lab; w/ Hal Daum\'e III
\end{itemize}

\textbf{Ph.D. University of California, Los Angeles}, CA, USA \hfill {2017.09 - 2021.12}
	% \begin{itemize}
	% \item Major: Natural Language Processing, Machine Learning; Dept.~of Computer Science
	% \end{itemize}
     \begin{itemize}[leftmargin=20pt]
    	\item[] Dept.~of Computer Science
     \item[] UCLANLP Group; w/ Kai-Wei Chang
    \end{itemize}

\textbf{Ph.D. University of Virginia (transferred)}, VA, USA \hfill 2016.08 - 2017.08
	% \begin{itemize}
	% \item Major: Natural Language Processing, Machine Learning; Dept.~of Computer Science
	% \end{itemize}

\textbf{M.S. Beihang University}, Beijing, China \hfill 2013.09 - 2016.01
	\begin{itemize}[leftmargin=20pt]
	\item[] Major: Virtualization, Data Mining; School of Computer Science and Engineering
	\end{itemize}

\textbf{B.S. Beihang University}, Beijing, China \hfill 2009.09 - 2013.07
	\begin{itemize}[leftmargin=20pt]
	\item[] Major: Computer Science and Engineering; School of Advanced Engineering
	\end{itemize}

%\subsection*{Internships}
%\hr
\textbf{Google Research} \hfill 2021.06 - 2021.09
\begin{itemize}[leftmargin=20pt]
\item[] Intern, SIR Responsible ML, New York City (Mentor: Xuezhi Wang; Yao Qin)
\end{itemize}

\textbf{Allen Institute for Artificial Intelligence} \hfill 2020.09 - 2020.12
\begin{itemize}[leftmargin=20pt]
\item[] Part-time Intern, Aristo team, Seattle (Mentor: Daniel Khashabi)
\end{itemize}

\textbf{Microsoft} \hfill 2020.06 - 2020.09
	\begin{itemize}[leftmargin=20pt]
	\item[] Intern, Microsoft Research, Redmond (Mentor:  Chris Brockett)
	\end{itemize}
	
\textbf{Microsoft} \hfill 2019.06 - 2019.09
	\begin{itemize}[leftmargin=20pt]
	\item[] Intern, Microsoft Research, Redmond (Mentor: Ahmed Hassan Awadallah)
	\end{itemize}
	
\textbf{DiDi Chuxing} \hfill 2016.01 - 2016.05
	\begin{itemize}[leftmargin=20pt]
	\item[] Intern, DiDi Chuxing Research, Beijing (Mentor: Pinghua Gong)
	\end{itemize}



%----------------------------------------------------------------------------------------
%	Honors, Awards, and Scholarships
%----------------------------------------------------------------------------------------
\section*{Honors, Awards, and Scholarships}
\hr
\begin{enumerate}
\item Computing Innovation Fellows \hfill 2021
\item Rising stars in EECS \hfill 2021
\item Microsoft PhD Fellowship \hfill 2020
\item SoCalNLP Symposium 2018 Best Poster Award \hfill 2018
\item UCLA Graduate Division Fellowships \hfill 2017
\item EMNLP 2017 Best Long Paper Award \hfill 2017
\item Outstanding Graduate of Beijing City \hfill 2016
\item Master Thesis Award \hfill 2016
\item 2nd Prize University Level Scholarship \hfill 2013, 2014, 2015
\item Outstanding Graduate, Beihang University. 6/236.	 \hfill 2014
\item National Scholarship. 2/236. \hfill 2014
\item The Award of `` Outstanding Graduates'' of Beihang University \hfill 2013
\item Special Scholarship for Freshmen. Top 6 of all freshmen (around 3000). \hfill 2009

\end{enumerate}

%----------------------------------------------------------------------------------------
%	Research Interests and Patent
%----------------------------------------------------------------------------------------
\section*{Publications}
\hr
 \hspace{0.1in}\textbf{Pre-print}
 	\begin{enumerate}
	\item J. Qu, L. Li, \textbf{J. Zhao}, S. Dev, K.-W. Chang. DisinfoMeme: A Multimodal Dataset for Detecting Meme Intentionally Spreading Out Disinformation. 
	\end{enumerate}

% \newpage
 \hspace{0.1in}\textbf{Published}
\begin{enumerate}
	\item Sandra Sandoval, \me, Marine Carpuat, Hal Daume. A Rose by Any Other Name would not Smell as Sweet: Social Bias in Name Mistranslations. EMNLP 2023.
    \item Yixin Wan, \me, Aman Chadha, Nanyun Peng,  Kai-Wei Chang. Are Personalized Stochastic Parrots More Dangerous? Evaluating Persona Biases in Dialogue Systems. EMNLP 2023 Findings.
    \item Ruyuan Zuo,  \me. Mind What You Measure For: A Study on Reliability of Prompt-Based Bias Measurement. WiNLP 2023.
    \item Ruijie Zheng, Xiyao Wang, Yanchao Sun, Shuang Ma, \me, Huazhe Xu, Hal Daume, Furong Huang. TACO: Temporal Latent Action-Driven Contrastive Loss For Visual Reinforcement Learning. NeurIPS 2023.
   
	\item H. An, Z. Li, \textbf{J. Zhao}, R. Rudinger. SODAPOP: Open-Ended Discovery of Social Biases in Social Commonsense Reasoning Models. EACL 2023.
 	\item A. Ovalle, S. Dev, \textbf{J. Zhao}, M. Sarrafzadeh, K.-W. Chang. Auditing Algorithmic Fairness in Machine Learning for Health with Severity-Based LOGAN. AAAI 2023 Health Intelligence Workshop.
	\item \textbf{J. Zhao}, X. Wang, Y. Qin, J. Chen, K.-W. Chang. Investigating Ensemble Methods for Model Robustness Improvement of Text Classifiers. EMNLP Findings, 2022.
	\item S. Dev, E. Sheng, \textbf{J. Zhao},  A. Smstutz, J. Sun, Y. Hou, M. Sanseverino, J. Kim, A. Nishi, N. Peng, K.-W. Chang. On Measures of Biases and Harms in NLP. AACL 2022.
	\item A.  Kwako, E. Wan, \textbf{J. Zhao}, K.-W. Chang, L. Cai, and M. Hansen. Using Item Response Theory to Measure Gender and Racial Bias of a BERT-based Automated English Speech Assessment System. BEA-2022: 17th Workshop on Innovative Use of NLP for Building Educational Applications, NAACL 2022.
	\item \textbf{J. Zhao}, D. Khashabi, T. Khot, A. Sabharwal, K.-W. Chang. Ethical-Advice Taker: Do Language Models Understand Natural Language Interventions? ACL Findings, 2021.
	\item C. Zhang, \textbf{J. Zhao}, H. Zhang, K.-W. Chang, C.-J. Hsieh. Double Perturbation: On the Robustness of Robustness and Counterfactual Bias Evaluation. NAACL, 2021.
	\item \textbf{J. Zhao}, and K.-W. Chang. LOGAN: Local Group Bias Detection by Clustering. Conference on Empirical Methods in Natural Language Processing (EMNLP), 2020. 
	\item \textbf{J. Zhao}, S. Mukherjee, S. Hosseini, K.-W. Chang, and A. H. Awadallah. Gender Bias in Multilingual Embeddings and Cross-Lingual Transfer. Association for Computational Linguistics (ACL), 2020.
	\item Y. Zhou, J-Y. Jiang, \textbf{J. Zhao}, K.-W. Chang, and W. Wang. "The Boating Store Had Its Best Sail Ever": Pronunciation-attentive Contextualized Pun Recognition. Association for Computational Linguistics (ACL), 2020.
	\item S. Jia*, T. Meng*, \textbf{J. Zhao}, and K.-W. Chang. Mitigating Gender Bias Amplification in Distribution by Posterior Regularization. Association for Computational Linguistics (ACL), 2020.
	\item A. Gaut, T. Sun, S. Tang, Y. Huang, J. Qian, M. ElSherief, \textbf{J. Zhao}, D. Mirza, E. Belding, K.-W. Chang, and W. Y. Wang. Towards Understanding Gender Bias in Relation Extraction. Association for Computational Linguistics (ACL), 2020.
	\item Z. Fu, Y. Xian, R. Gao, \textbf{J. Zhao}, Q. Huang, Y. Ge, S. Xu, S. Geng, C. Shah, Y. Zhang, G. de Melo. Fairness-Aware Explainable Recommendation over Knowledge Graphs.  Proceedings of the 43rd International ACM SIGIR Conference on Research and Development in Information Retrieval (SIGIR), 2020.
	\item T. Wang, \textbf{J. Zhao},  M. Yatskar, K. Chang, V. Ordonez. Balanced Datasets Are Not Enough: Estimating and Mitigating Gender Bias in Deep Image Representations. International Conference on Computer Vision (ICCV), 2019
	\item P. Zhou, W. Shi, \textbf{J. Zhao}, K.-H. Huang, M. Chen, K.-W. Chang. Examining Gender Bias in Languages with Grammatical Gender. Conference on Empirical Methods in Natural Language Processing \& International Joint Conference on Natural Language Processing (EMNLP-IJCNLP), 2019
	\item T. Sun, A. Gaut, S. Tang, Y. Huang, M. ElSherief, \textbf{J. Zhao}, M. Diba, B. Elizabeth, K.-W. Chang and W.Y. Wang. Mitigating Gender Bias in Natural Language Processing: Literature Review. Association for Computational Linguistics (ACL), 2019
	\item \textbf{J. Zhao}, T. Wang, M. Yatskar, R. Cotterell , V. Ordonez, K.-W. Chang. Gender Bias in Contextualized Word Embeddings. North American Chapter of the Association for Computational Linguistics (NAACL), 2019
	\item \textbf{J. Zhao}, Y. Zhou, Z. Li, W. Wei, K.-W. Chang. Learning Gender Neutral Word Embeddings. Conference on Empirical Methods in Natural Language Processing (EMNLP), 2018
	\item \textbf{J. Zhao}, T. Wang, M. Yatskar, V. Ordonez, K.-W. Chang. Gender Bias in Coreference Resolution: Evaluation and Debiasing Methods. North American Chapter of the Association for Computational Linguistics (NAACL), 2018
	\item \textbf{J. Zhao}, T. Wang, M. Yatskar, V. Ordonez, K.-W. Chang. Men Also Like Shopping: Reducing Gender Bias Amplification using Corpus-level Constraints. Conference on Empirical Methods in Natural Language Processing (EMNLP), 2017 {\color{red}\textbf{(Best Long Paper Award)}}
	\item \textbf{J. Zhao}, J. Li, B. Zhou, F. Chen, P. Tomchik, W. Ju. Parallel Algorithms for Anomalous Subgraph Detection. Concurrency and Computation: Practice and Experience, 29(3), e3769. 2017
	\item J. Li, \textbf{J. Zhao}, Y. Li, L. Cui, B. Li, L. Liu, J. Panneerselvam. iMIG: Toward an Adaptive Live Migration Method for KVM Virtual Machines. The Computer Journal, 58(6), 1227-1242. 2015
	\item B. Shi, B. Li, L. Cui, \textbf{J. Zhao}, J. Li. SyncSnap: Synchronized Live Memory Snapshots of Virtual Machine Networks. IEEE International Conference on High Performance Computing and Communications (HPCC), 2014
\end{enumerate}

\iffalse
\vspace{0.5em}
\hspace{0.32in}\textbf{Patent}
\begin{enumerate}
	\item 1.	B. Shi, B. Li, \textbf{J. Zhao}. An Algorithm for the Migration of ARM Virtual Machines. Patent Number: 83995027CN0. (submitted)
\end{enumerate}
\fi


%----------------------------------------------------------------------------------------
%	Talks
%----------------------------------------------------------------------------------------
\section*{Talks and Panels}
\hr
\begin{itemize}
\item Invited talk @CHAI in UChicago. \hfill 2023.03
\item Trustworthy and Responsible AI: Fairness, Interpretability, Transparency and Their Interactions. AAAI tutorial. \hfill 2023.02
\item Gender Bias in Natural Language Processing Workshop \hfill 2021.08
\item Talk @Apple Research. \hfill 2020.08
\item AKBC KG-BIAS Workshop \hfill 2020.06
\item Gender Equality and Corporate Social Responsibility, UN-Women China \hfill 2019.11
\item Grace Hopper Celebration \hfill 2018.09
\item NLP Highlights Podcast \hfill 2018.08
\item Mid-Atlantic Student Colloquium on Speech, Language and Learning   \hfill 2017.05
\end{itemize}

%----------------------------------------------------------------------------------------
%	Professional Activities
%----------------------------------------------------------------------------------------
\section*{Professional Activities}
\hr
Organizer:
\begin{itemize}
\item Workflow Chair, AAAI 2023
\item Women in Machine Learning (WiML), NeurIPS 2021. 
\item Workshop on Socially Responsible Machine Learning, ICML 2021.
\item NLP for Positive Impact Workshop, ACL 2021, EMNLP 2022
\end{itemize}
Program Committee/Reviewer:
\begin{itemize}
\item Area Chair: EMNLP 2023
\item NeurIPS 2023
\item AACL 2022
\item ARR 2021, 2022
\item TrustNLP workshop 2021, 2022
\item NAACL 2019, 2021, 2022
\item ACL 2020, 2021
\item AAAI 2020, 2021
\item EMNLP 2018,  2021, 2022
\item NLPCC-English 2018, 2019, 2020
\item NLPCC-Chinese 2018, 2 019
\item AKBC 2019
\end{itemize}

%----------------------------------------------------------------------------------------
%	Teaching Experience
%----------------------------------------------------------------------------------------
\section*{Teaching Experience}
\hr

\textbf{USC}
\begin{itemize}
\item CSCI 699, Ethics in NLP \hfill 2023 Fall
\end{itemize}

\textbf{Guest Lecture}
\begin{itemize}
\item CSCI 697, USC \hfill 2023.08
\item CMSC 396H, UMD \hfill 2022.10
\item CSCI 544, USC \hfill 2022.04
\item CS seminar (w/ 200 enrollment, show case of EDI research), UCLA \hfill 2021.12
\item IST 597, PSU \hfill  2021.11
\item CSE 290C, UCSC \hfill  2021.05
\item CS263, UCLA \hfill  2021.03
\item Ethics and Fairness in AI, UPitt \hfill  2021.02
\end{itemize}

\textbf{UCLA}
\begin{itemize}
	\item Teaching Assistant, Introduction to Machine Learning, Kai-Wei Chang. \hfill 2019 Fall
\end{itemize}
\textbf{University of Virginia}
\begin{itemize}
\item Teaching Assistant, Algorithm, Kong-Cheng Wong. \hfill 2017 Spring
\item Teaching Assistant, Software Development Methods, Nada Basit and David Edwards. \hspace*{\fill} 2017 Spring 
\item Teaching Assistant, Algorithm, Gabriel Robins. \hfill  2016 Fall
\item Teaching Assistant, Discrete Math, David Edwards. \hfill 2016 Fall
\end{itemize}

%\section*{Others}
%\hr
%\begin{itemize}
%\item Programming language: Python
%\end{itemize}


\end{document}
