\documentclass[11pt, a4paper]{article}

\usepackage[a4paper, margin=1.0in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{tgpagella} 
%\usepackage{indentfirst}
\usepackage{fancyhdr}
\setlength\parindent{0pt}

\usepackage{xcolor}
\definecolor{dark-blue}{rgb}{0.15, 0.15, 0.4}

\usepackage{sectsty}
\sectionfont{\large\bf\uppercase}

\usepackage{titlesec}
\titlespacing*{\section}{0.0em}{0.2em}{0.0em}

\usepackage{enumitem}
\setlist[itemize]{leftmargin=0.5in, itemsep=-0.5\parsep, topsep=-0.5\parskip}
\setlist[enumerate]{leftmargin=0.5in, itemsep=-0.5\parsep, topsep=-0.5\parskip}


\renewcommand{\baselinestretch}{1.04}
%\setlength{\parskip}{0.4em}
\newcommand\nl[1]{\item[] {#1}}
\newcommand\ml[1]{\item[--] {#1}}
\newcommand\pl[1]{\vspace{-0.2em}\begin{sloppypar}{#1}\end{sloppypar}}
\newcommand{\hr}{\hrule\vspace{0.5em}}

\pagestyle{empty}
%\rhead{Last Updated: \today}
\renewcommand{\headrulewidth}{0pt}

\begin{document}
\thispagestyle{fancy}	

\begin{center}
	{\large \bf Jieyu Zhao}
\end{center}
\begin{center}
	{368 ENG VI, UCLA, CA | {https://jyzhao.net} | {jieyuzhao@ucla.edu}}
\end{center}

%----------------------------------------------------------------------------------------
%	Research Interests
%----------------------------------------------------------------------------------------
\section*{Research Interests}
\hr
\begin{itemize}
\item Detecting potential stereotypes in machine learning models
\item Developing computational approaches to enhance the fairness in NLP applications
\end{itemize}


%----------------------------------------------------------------------------------------
%	Education
%----------------------------------------------------------------------------------------
\section*{Education And Experience}
\hr
\textbf{Ph.D. University of California, Los Angele}, CA, USA \hfill {2017.09 - current}
%	\begin{itemize}
%	\item Major: Natural Language Processing, Machine Learning; Dept.~of Computer Science
%	\end{itemize}

\textbf{Ph.D. University of Virginia (withdrawal)}, VA, USA \hfill 2016.08 - 2017.08
%	\begin{itemize}
%	\item Major: Natural Language Processing, Machine Learning; Dept.~of Computer Science
%	\end{itemize}

\textbf{M.S. Beihang University}, Beijing, China \hfill 2013.09 - 2016.01
%	\begin{itemize}
%	\item Major: Virtualization, Data Mining; School of Computer Science and Engineering
%	\end{itemize}

\textbf{B.S. Beihang University}, Beijing, China \hfill 2009.09 - 2013.07
%	\begin{itemize}
%	\item Major: Computer Science and Engineering; School of Advanced Engineering
%	\end{itemize}
	
\

\textbf{Allen Institute for Artificial Intelligence, Seattle} \hfill 2020.09 - 2020.12
%\begin{itemize}
%\item Part-time Intern, Aristo team, Seattle
%\end{itemize}

\textbf{Microsoft Research, Redmond} \hfill 2020.06 - 2020.09
%	\begin{itemize}
%	\item Intern, Microsoft Research, Redmond 
%	\end{itemize}
	
\textbf{Microsoft Research, Redmond} \hfill 2019.06 - 2019.09
%	\begin{itemize}
%	\item Intern, Microsoft Research, Redmond 
%	\end{itemize}
	
%\textbf{DiDi Chuxing} \hfill 2016.01 - 2016.05
%	\begin{itemize}
%	\item Intern, DiDi Chuxing Research, Beijing 
%	\end{itemize}



%----------------------------------------------------------------------------------------
%	Research Interests and Patent
%----------------------------------------------------------------------------------------
\section*{Publications and Patent}
\hr
\hspace{0.32in}\textbf{Publications}
\begin{enumerate}
	\item C. Zhang, \textbf{J. Zhao}, H. Zhang, K.-W. Chang, C.-J. Hsieh. Double Perturbation: On the Robustness of Robustness and Counterfactual Bias Evaluation. NAACL, 2021.
	\item \textbf{J. Zhao}, and K.-W. Chang. LOGAN: Local Group Bias Detection by Clustering. EMNLP, 2020. 
	\item \textbf{J. Zhao}, S. Mukherjee, S. Hosseini, K.-W. Chang, and A. H. Awadallah. Gender Bias in Multilingual Embeddings and Cross-Lingual Transfer. ACL, 2020.
	\item Y. Zhou, J-Y. Jiang, \textbf{J. Zhao}, K.-W. Chang, and W. Wang. "The Boating Store Had Its Best Sail Ever": Pronunciation-attentive Contextualized Pun Recognition. ACL, 2020.
	\item S. Jia*, T. Meng*, \textbf{J. Zhao}, and K.-W. Chang. Mitigating Gender Bias Amplification in Distribution by Posterior Regularization.  ACL, 2020.
	\item A. Gaut, T. Sun, S. Tang, Y. Huang, J. Qian, M. ElSherief, \textbf{J. Zhao}, D. Mirza, E. Belding, K.-W. Chang, and W. Y. Wang. Towards Understanding Gender Bias in Relation Extraction.  ACL, 2020.
	\item Z. Fu, Y. Xian, R. Gao, \textbf{J. Zhao}, Q. Huang, Y. Ge, S. Xu, S. Geng, C. Shah, Y. Zhang, G. de Melo. Fairness-Aware Explainable Recommendation over Knowledge Graphs.   SIGIR,  2020.
	\item T. Wang, \textbf{J. Zhao},  M. Yatskar, K. Chang, V. Ordonez. Balanced Datasets Are Not Enough: Estimating and Mitigating Gender Bias in Deep Image Representations. ICCV, 2019
	\item P. Zhou, W. Shi, \textbf{J. Zhao}, K.-H. Huang, M. Chen, K.-W. Chang. Examining Gender Bias in Languages with Grammatical Gender. EMNLP-IJCNLP, 2019
	\item T. Sun, A. Gaut, S. Tang, Y. Huang, M. ElSherief, \textbf{J. Zhao}, M. Diba, B. Elizabeth, K.-W. Chang and W.Y. Wang. Mitigating Gender Bias in Natural Language Processing: Literature Review.  ACL, 2019
	\item \textbf{J. Zhao}, T. Wang, M. Yatskar, R. Cotterell , V. Ordonez, K.-W. Chang. Gender Bias in Contextualized Word Embeddings.  NAACL, 2019
	\item \textbf{J. Zhao}, Y. Zhou, Z. Li, W. Wei, K.-W. Chang. Learning Gender Neutral Word Embeddings.  EMNLP, 2018
	\item \textbf{J. Zhao}, T. Wang, M. Yatskar, V. Ordonez, K.-W. Chang. Gender Bias in Coreference Resolution: Evaluation and Debiasing Methods.  NAACL, 2018
	\item \textbf{J. Zhao}, T. Wang, M. Yatskar, V. Ordonez, K.-W. Chang. Men Also Like Shopping: Reducing Gender Bias Amplification using Corpus-level Constraints. EMNLP, 2017 {\color{red}\textbf{(Best Long Paper Award)}}
%	\item \textbf{J. Zhao}, J. Li, B. Zhou, F. Chen, P. Tomchik, W. Ju. Parallel Algorithms for Anomalous Subgraph Detection. Concurrency and Computation: Practice and Experience, 29(3), e3769. 2017
%	\item J. Li, \textbf{J. Zhao}, Y. Li, L. Cui, B. Li, L. Liu, J. Panneerselvam. iMIG: Toward an Adaptive Live Migration Method for KVM Virtual Machines. The Computer Journal, 58(6), 1227-1242. 2015
%	\item B. Shi, B. Li, L. Cui, \textbf{J. Zhao}, J. Li. SyncSnap: Synchronized Live Memory Snapshots of Virtual Machine Networks. IEEE International Conference on High Performance Computing and Communications (HPCC), 2014
\end{enumerate}

\iffalse
\vspace{0.5em}
\hspace{0.32in}\textbf{Patent}
\begin{enumerate}
	\item 1.	B. Shi, B. Li, \textbf{J. Zhao}. An Algorithm for the Migration of ARM Virtual Machines. Patent Number: 83995027CN0. (submitted)
\end{enumerate}
\fi
%----------------------------------------------------------------------------------------
%	Honors, Awards, and Scholarships
%----------------------------------------------------------------------------------------
\section*{Honors, Awards, and Scholarships}
\hr
\begin{enumerate}
\item Microsoft PhD Fellowship \hfill 2020
\item SoCalNLP Symposium 2018 Best Poster Award \hfill 2018
\item UCLA Graduate Division Fellowships \hfill 2017
\item EMNLP 2017 Best Long Paper Award \hfill 2017
\item Outstanding Graduate of Beijing City \hfill 2016
\item Master Thesis Award \hfill 2016
\item 2nd Prize University Level Scholarship \hfill 2013, 2014, 2015
\item Outstanding Graduate, Beihang University. 6/236.	 \hfill 2014
\item National Scholarship. 2/236. \hfill 2014
\item The Award of `` Outstanding Graduates'' of Beihang University \hfill 2013
\item Special Scholarship for Freshmen. Top 6 of all freshmen (around 3000). \hfill 2009

\end{enumerate}


%----------------------------------------------------------------------------------------
%	Talks
%----------------------------------------------------------------------------------------
\section*{Talks}
\hr
\begin{itemize}
\item Guest spekaer @CS263, UCLA, March 2021
\item Guest speaker @Ethics and Fairness in AI, UPitt,  Feburary 2021
\item AKBC KG-BIAS workshop, 2020
\item Gender Equality and Corporate Social Responsibility hosted by UN-Women China, November 2019 
\item Grace Hopper Celebration, September 2018
\item NLP highlights podcast, August 2018
\item Mid-Atlantic Student Colloquium on Speech, Language and Learning (MASC-SLL), May 2017
\end{itemize}

%----------------------------------------------------------------------------------------
%	Professional Activities
%----------------------------------------------------------------------------------------
\section*{Professional Activities}
\hr
Organizer:
\begin{itemize}
\item Workshop on Socially Responsible Machine Learning, ICML 2021.
\item NLP4positive workshop, ACL 2021
\end{itemize}
Program Committee/Reviewer:
\begin{itemize}
\item TrustNLP workshop, NAACL 2021
\item NAACL 2021, 2019
\item ACL 2021, 2020
\item AAAI 2019
%\item Secondary reviewer EMNLP 2018
\item NLPCC-English 2020, 2019, 2018
\item NLPCC-Chinese 2019, 2018
\end{itemize}

%----------------------------------------------------------------------------------------
%	Teaching Experience
%----------------------------------------------------------------------------------------
\section*{Teaching Experience}
\hr
\textbf{UCLA}
\begin{itemize}
	\item Teaching Assistant, Introduction to Machine Learning, Kai-Wei Chang. 2019 Fall
\end{itemize}
\textbf{University of Virginia}
\begin{itemize}
\item Teaching Assistant, Algorithm, Kong-Cheng Wong. 2017 Spring
\item Teaching Assistant, Software Development Methods, Nada Basit and David Edwards. 2017 Spring
\item Teaching Assistant, Algorithm, Gabriel Robins. 2016 Fall
\item Teaching Assistant, Discrete Math, David Edwards. 2016 Fall
\end{itemize}

%\section*{Others}
%\hr
%\begin{itemize}
%\item Programming language: Python
%\end{itemize}


\end{document}

